---
title: "RV144 Aids trials"
author: "instr"
date: "April 13, 2016"
output: html_document
---


# Thailand Aids study
```{r include=FALSE}
require(tigerstats)
```

## Introduction

In the late 1980s in Thailand, there was a dramatic increase in the prevalence of infection with the human immunodeficiency virus type 1 (HIV-1) in sentinel surveillance cohorts.1-3 Initially, these groups consisted of injection-drug users and commercial sex workers; they were subsequently expanded to include persons in the general population. By 1995, the overall seroprevalence of HIV-1 reached a peak of 3.7% among conscripts in the Royal Thai Army and of 12.5% among conscripts from Northern Thailand.2,4,5 The Thai Ministry of Public Health responded with an effective HIV-prevention campaign, and the number of new HIV-1 infections per year decreased from an estimated 143,000 in 1990 to 14,000 in 2007.2,4,6-9 The persistence of new infection despite these measures led public health officials to conclude that an HIV vaccine, within the context of a broader HIV-prevention program, was needed for better control of the epidemic.



## Methods and data

Study Design and Population
This study was a community-based, randomized, multicenter, double-blind, placebo-controlled efficacy trial of the prime–boost combination of vaccines containing ALVAC-HIV (vCP1521) (Sanofi Pasteur) and AIDSVAX B/E (Global Solutions for Infectious Diseases). For details regarding the vaccines and placebo, see the Supplementary Appendix, available with the full text of this article at NEJM.org. The study was designed to evaluate two coprimary end points: the prevention of HIV-1 infection and the effect of vaccination on the early viral load after infection. The trial was conducted through facilities of the Thai Ministry of Public Health in Rayong and Chon Buri provinces. From September 2003 through December 2005, a total of 16,402 volunteers were enrolled.
Thai men and women who were between the ages of 18 and 30 years and who were not infected with HIV were recruited from the community without regard to HIV risk (i.e., community risk). Written informed consent was obtained from all volunteers, who were required to pass a written test of understanding. Women were counseled to practice effective contraception until 3 months after the last vaccination; pregnant and breast-feeding women were excluded.

###Study Design and Population
This study was a community-based, randomized, multicenter, double-blind, placebo-controlled efficacy trial of the prime–boost combination of vaccines containing ALVAC-HIV (vCP1521) (Sanofi Pasteur) and AIDSVAX B/E (Global Solutions for Infectious Diseases). For details regarding the vaccines and placebo, see the Supplementary Appendix, available with the full text of this article at NEJM.org. The study was designed to evaluate two coprimary end points: the prevention of HIV-1 infection and the effect of vaccination on the early viral load after infection. The trial was conducted through facilities of the Thai Ministry of Public Health in Rayong and Chon Buri provinces. From September 2003 through December 2005, a total of 16,402 volunteers were enrolled.
Thai men and women who were between the ages of 18 and 30 years and who were not infected with HIV were recruited from the community without regard to HIV risk (i.e., community risk). Written informed consent was obtained from all volunteers, who were required to pass a written test of understanding. Women were counseled to practice effective contraception until 3 months after the last vaccination; pregnant and breast-feeding women were excluded.

###Primary End Points
HIV-1 Infection
HIV-1 infection was diagnosed in 132 subjects (56 in the vaccine group and 76 in the placebo group) during 52,985 person-years of follow-up in the intention-to-treat analysis, in 86 subjects (36 in the vaccine group and 50 in the placebo group) during 36,720 person-years of follow-up in the per-protocol analysis, and in 125 subjects (51 in the vaccine group and 74 in the placebo group) during 52,985 person-years of follow-up in the modified intention-to-treat analysis. One subject in the placebo group who was identified by hospital record as being seropositive for HIV after dying from Pneumocystis jirovecii pneumonia was included in the analysis before the unblinding of the study. This diagnosis of HIV-1 infection was the only one that occurred outside planned procedures.
We create the following data set

```{r}
groupsize = 16402
subgp = groupsize/2
vacine = c(subgp-51,51)
placebo =  c(subgp-74,74)
results = as.table(cbind(vacine,placebo))
rownames(results) <- c("none","aids")

```


## Results
<!-- You are to add descriptive comments to explain to the reader what the plot is showing !-->
The plot is showing how a group of 16,000 people were distributed into two evenly different groups. Both groups were tested for aids. One groups was injected with a vaccine against aids. The other groups was injected with a placebo which was a saline solution. The people getting injecting the solutions and the actual patients were not informed with what they have been injected with, two years passed and they were brought back in and tested again to see if they have had aids. Below we will see the number of people that got aids in both of the groups.
### Graphical results
<!--Display graphical evidence as to the effectiveness of the vaccine with explanations!-->
```{r}
barchartGC(results,type = "percent")
```
If the same number were correct, saying that the group had the same amount of people then the precentages should be about the same, but because there is a significant diiference between these two groups it shows us that something isn't right. The numbers on the left represent the amount of people that had these injections with eithera placebo or a vaccine and didn't have aids. The bar chart on the right represents the number of people that had the vaccines and placebos that that has aids. They should be the same but because they are not it shows us that something is not right. 

### Numerical Results

<!--Display numerical evidence as to the effectiveness of the vaccine with explanations !--> 

```{r}
colPerc(results)
rowPerc(results)
```
When the group of patients got split up and put into two different groups, the numbers on top show us after two years they got retested and in one groupd 40% of people with the vaccine got aids. In the other group that got the placebo about 60% of people got aids. So the vaccine seemed to be working for about 20% of these people, but like we will see in the later research the chances of us getting this number again will be 0.04%.



## Inferential results

<!--Display inferential evidence as to the effectiveness of the vaccine with explanations and interpretations!-->

```{r}
chisqtestGC(results, graph = TRUE)
```


## Conclusions

<Summarise your results as to the effectiveness of the vaccine with explanations that could be understood by your mom>